---
title: "P8160_project_1"
author: "Chunxiao Zhai"
date: "2/6/2019"
output: html_document
---

```{r setup, include=FALSE}
set.seed(816001)
library(coxed)
knitr::opts_chunk$set(echo = TRUE)
```

from syllabus: 

Each report should include (1) A description of the statistical problem to be addressed; (2) A general description of the approach taken, along with some justication for the direction taken;(3) Conclusions, along with supporting output (typically including graphics); (4) The complete code.

project requirement:

Your tasks: Design a simulation study to evaluate the impacts of misspecifying the baseline hazard function
on the estimate of the treatment effect, and one could avoid this issue by using a semi-parametric Cox model.
In the meantime, investigate the impact of fitting too complicated a model when an exponential is sufficient

published studies:
The simulation study would include data simulated under various distributions such as exponential, Weibull, log-normal, log-logistic and with different sample sizes and effect sizes, to evaluate power, type I error rate and precision of the estimated coefficient.

#step 1. generate data
1.1 derivation of the t fomular (Ren):

n
miu
randome error

1) decay rate miu = 1
2) decay rate miu = 2
3) decay rate miu = 0.5

1.2 plot to confirm good randomnes

plot1
plot2
plot2

#step 2. fit different data into different model and get estimation points

1) Exponential
2) Weibull
3) Cox

test goodness of fit for different model,

estimation perfomance: invaraince(sample size), accuracy(bias vs variance)
plots/table:

AIC
CI and p-Value

same simulation dataset in different models survplots,

published studies:
The simulation study would include data simulated under various distributions such as exponential, Weibull, log-normal, log-logistic and with different sample sizes and effect sizes, to evaluate power, type I error rate and precision of the estimated coefficient.


### R codes for Hazard Ratio Estimation
```{r, eval=F, echo=T}
# Exponential
fit.exponential <- survreg(Surv(y) ~ x[, 1] + x[, 2], dist = "exponential")
summary(fit.exponential)
- fit.exponential$coefficients[-1]

# Weibull
fit.weibull <- survreg(Surv(y) ~ x[, 1] + x[, 2], dist = "weibull")
summary(fit.weibull)
- fit.weibull$coefficients[-1] / fit.weibull$scale

# Cox
fit.cox <- coxph(Surv(y) ~ x[, 1] + x[, 2])
summary(fit.cox)
```


